Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

To perform simple statistical estimations on counts measurements,
CountsStatistic classes encapsulate the aforementioned statistic functions to
measure excess counts and estimate the associated statistical significance,
errors and upper limits. They perform maximum likelihood ratio tests to
estimate significance (the square root of the statistic difference) and compute
likelihood profiles to measure errors and upper limits. The code example
\ref{codeexample:stats} shows how to compute the Li \& Ma
significance~\citep{LiMa} of a set of measurements.

>>>>

To perform simple statistical estimations on counts measurements,
\code{CountsStatistic} classes encapsulate the aforementioned statistic functions to
measure excess counts and estimate the associated statistical significance,
errors and upper limits. They perform maximum likelihood ratio tests to
estimate significance (the square root of the statistic difference) and compute
likelihood profiles to measure errors and upper limits. The code example
\ref{codeexample:stats} shows how to compute the Li \& Ma
significance~\citep{LiMa} of a set of measurements.
